%change page layout to floating and centered with central title 

%Acknowledgements:
	%Azadeh : support well beyond the thesis/required role, friendship, counsel and insightful discussions o/
	%Csaba and Tor : as the primary source, providing an approachable work for neophytes, making spring-boarding 			easy o/
	%Rachel: for proof reading and support  o/
	%Jenny Wadsworth: for advice, support and chapperoning o/
	%Daniel Elton for providing the solution to many problems ? :p 
	%Erick Chacon Montalvan, Andrew R. Dalton for their thesis templates, which served as the basis for this thesis's 		template and title page o/
	
{\centering 
{ \huge Acknowledgments}\\
\vspace{5em}
The author wishes for his gratitude to the following people to be publicly known. 
\hfill
\par First and foremost, the author is grateful to dr. Azadeh Khaleghi, his supervisor, for her help well beyond this dissertation. Her recommended readings, wether related to this topic or another, provided valuable knowledge and understanding on a wealth of topics. Friendly conversations on a range of machine learning topics in her office strengthened the resolve of the author to pursue it as a career. Here too, her advice proved invaluable and the author is greatly indebted to her. 
\par For her thoughtful advice and regular support throughout his studies, the author thanks dr. Jenny Wadsworth, his academic advisor.  
\par For her proof-reading and shared passion for typography and elegant language, the author thanks his fellow student, Rachel Bessant, who assisted him many times beyond this thesis.  
\par The author would like to also acknowledge and thank, while not knowing them personally, both Erick C. Montalvan and Andrew R. Dalton, the former's enhancements of the later's {\LaTeX } dissertation template\footnote{To be found at {\url{https://github.com/ErickChacon/lancs-thesis}}.} provided the ground work for the typography of this thesis. As both are public templates, this thesis' template will be released in future under a public license, for the benefit of future students. 
\par Finally the author would like to acknowledge dr. Tor Lattimore and Pr. Csaba Szepesv{\'a}ri for their blog {\href{http://banditalgs.com}{{\em Bandit Algorithms}}} which provided the main body of research for this thesis and much of its proofs, theorems and many elements of notation. As it set out with different goals, the contents of this thesis have been rearranged, modified, and restyled to what the author deems best, however he is indebted for the quality of their approachable work which greatly contributed to his understanding. 
}

	
\vfill